Radio Emission from Red-Giant Hot Jupiters

### 2015-12-29 ms.tex
a few final touches, mainly wording changes. --tony

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbp]
   \plotoneh{cartoon2_5Mj_100pc_smooth.pdf}
%\begin{figure*}[tbp]
%   \plotonesc{cartoon_10Mj_100pc_smooth.pdf}
   \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_{\rm J}$ and the host red giants with 100 $R_{\odot }$.
     The spectrum of RGHJ is modeled after Jovian radio spectra, e.g. Figure 8 of \citet{zarka_et_al2004} and Figure 2 of \citet{griesmeier2007a}; contribution from Io-DAM is not shown here.
     The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law.
     \revise{The shadowed region represents the frequency below the plasma frequency of the stellar wind.}}
  \label{fig:cartoon}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\revise{%
Once planetary radio emission is detected, it provides a unique approach for learning the planetary property.
As the auroral radio flux is significantly modulated in association with several physical processes described in \S\ref{ss:timevariability}, the time variability is useful to imply the planetary spin rotation period or the presence of satellites.
If spectra are obtained, the upper cut-off frequency can tell us the magnetic field strength of the planetary surfaces, which, when combined with constrains on the planetary mass via e.g. radial-velocity observations, tests  the proposed scaling law of planetary dynamo. 
Furthermore, the lower cut-off frequency of the RGHJ emission, which presumably corresponds to in situ plasma frequency, probes the stellar wind properties at the planetary orbit.
In addition, the planetary radio power in such an extreme environment as a RG's massive stellar wind will be valuable data points to test the empirical ``radiometric Bode's law''.
We also note that the radio emission of RGHJs may also be used as a tool for discovering/confirming new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars.
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbp]
   \plotoneh{cartoon2_5Mj_100pc_smooth.pdf}
%\begin{figure*}[tbp]
%   \plotonesc{cartoon_10Mj_100pc_smooth.pdf}
   \caption{A cartoon of the radio emission spectra of a RGHJ with 10$M_{\rm J}$ and the host red giants with 100 $R_{\odot }$.
     The spectrum of the RGHJ is modeled after Jovian radio spectra, e.g.\ Figure 8 of \citet{zarka_et_al2004} and Figure 2 of \citet{griesmeier2007a}; the contribution from Io-DAM is not shown here.
     The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law.
     \revise{The shaded region represents the portion of the spectrum below the plasma frequency of the stellar wind.}}
  \label{fig:cartoon}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\revise{%
Once planetary radio emission is detected, it provides a unique approach for studying the planet's property.
As the auroral radio flux is significantly modulated in association with several physical processes described in \S\ref{ss:timevariability}, the time variability is useful to infer the planetary spin rotation period or the presence of satellites.
If spectra are obtained, the upper cut-off frequency can tell us the magnetic field strength at the planetary surface, which, when combined with constraints on the planetary mass via e.g.\ radial-velocity observations, tests the proposed scaling law of planetary dynamo. 
Furthermore, the lower cut-off frequency of the RGHJ emission, which presumably corresponds to in situ plasma frequency, probes the stellar wind properties at the planetary orbit.
In addition, the planetary radio power in such an extreme environment as a RG's massive stellar wind will be valuable data points to test the empirical ``radiometric Bode's law''.
We also note that the radio emission of RGHJs may be used as a tool for discovering/confirming new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars.
}
